Here, we attempt to show that a data cube can be used to effectively index the relevant data for all interactions.
\subsection{Sketches}
\begin{claim}\label{alljoins}
Data cubes can be used to effectively index all manners of natural joins.
\end{claim}

\begin{sketch}
Claim~\ref{alljoins} can be shown by induction.\\
\textbf{Basis}: The following joins can be indexed effectively with data cubes:
\begin{enumerate}
	\item $X = A\bowtie{}B$
\end{enumerate}
\textbf{Inductive Hypothesis}: Relation $H$ can be indexed effectively with a data cube.\\
\textbf{Inductive Step}: In joining $H$ and another relation $I$, two possibilities arise.
\begin{enumerate}
	\item If the schemas of $H$ and $I$ do not share any common attributes, the data cube for $H$ must be expanded to include a new dimension for each attribute in $I$.
	Note, however, that this situation is unlikely to arise in DataViz as it results in a full cross product, and it does not really reveal anything new, information-theoretically.
	\item In the more common case, $H$ and $I$ share some attributes to be matched on the join.
	In this case, the data cube for $H$ must be expanded to include all attributes in $I$ which are not present in $H$ (i.e. all of the attributes in $I$ which do not participate in the join).
\end{enumerate}
In both cases, the new data cube effectively indexes the join \mbox{$H\bowtie{}I$}.
Noting that multijoins may be achieved commutatively, this inductive step describes joins of arbitrary complexity.
\end{sketch}

\begin{claim}
Data cubes can be used to effectively index all manners of interactions (where the data is drawn from a relational database).
\end{claim}

\begin{sketch}
Let the set of relations $\{Z_1, Z_2, \ldots, Z_n\}$ be the minimal set of relations representing joins and base tables which see all of the ``interacting" data, where interacting data is all of the data which participates in the interaction.
If the interaction is defined in terms of queries, this set will be a subset of \{the outermost joins from all of the queries\}.
From Claim~\ref{alljoins}, we know that each of the relations $Z_k$ can be effectively indexed with a data cube.
\end{sketch}
\subsection{Issues}
\begin{enumerate}
	\item What if an aggregation is joined with another relation?
	\item What about outer joins?
	\item What about two joins which each share one common base table?
\end{enumerate}